%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.3 (29/10/16)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com) with modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same 
% directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

%------ Set font for the whole doc

%\usepackage{DejaVuSans}
%\usepackage{tgadventor} %needs tlmgr_install("tex-gyre")
%\usepackage{lmodern}
%\usepackage[scaled=1.2]{libertine}
%\usepackage{lato}
\usepackage{fontawesome}
%\usepackage{palatino} %tlmgr_install("palatino")
%\usepackage{charter} %tlmgr_install("charter")
\renewcommand*\familydefault{\sfdefault} %% Only if the base font of the document is to be sans serif
\usepackage[T1]{fontenc}

%------ Set specific font for name and section
\newenvironment{myfont}{\fontfamily{bch}\selectfont}{\par} % select charter as special font
\DeclareTextFontCommand{\textmyfont}{\myfont} % replace text inside \textmyfont{} to charter

%\renewcommand{\sfdefault}{bch}

%------ Set theme

\moderncvstyle{classic} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{green} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

%\usepackage[scale=0.75]{geometry} % Reduce document margins
\usepackage[scale=0.8, top=2cm, bottom=2cm, left=2cm, right=2cm]{geometry}
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

%\usepackage[utf8]{inputenc}   


%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Gael} % Your first name
\familyname{Sola} % Your last name

% All information in this block is optional, comment out any lines you don't need
\title{Forestry and REDD+ \newline technical expert}
\address{House 81, 76/32 An Duong}{Tay Ho, Ha Noi, Viet Nam}
%\phone{+84 9 63 19 85 44 (vi)}
\mobile{+84 9 63 19 85 44 (vi)}
\mobiletwo{+33 6 42 85 08 31 (fr)}
%\fax{(000) 111 1113}
\email{gaelsola@hotmail.fr}
%\homepage{staff.org.edu/~jsmith}{staff.org.edu/$\sim$jsmith} % The first argument is the url for the clickable link, the second argument is the url displayed in the template - this allows special characters to be displayed such as the tilde in this example
\extrainfo{skype: gael.sola}
%\photo[70pt][0.4pt]{pictures/photo} % The first bracket is the picture height, the second is the thickness of the frame around the picture (0pt for no frame)
\quote{At the interface between countries technical experts and decision makers to improve forest management and protection}
%\quote{From better data to better decision-making for forest management and protection}

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	CURRICULUM VITAE
%----------------------------------------------------------------------------------------

\makecvtitle % Print the CV title


%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

%\vspace{-6pt}
\section{Experience}

\subsection{FAO - Food and Agriculture Organization of the United Nations}

%\cventry{2014--present}{Forestry and REDD+ technical expert}{UN-REDD Programme, Food and Agriculture Organization of the United Nations}{}{}{
\cventry{2014--present}{Forestry and REDD+ technical expert}{UN-REDD Programme}{Viet Nam and South-Southeast Asia}{}{
\begin{itemize}
\item Support the development of improved \textbf{forest monitoring} in Viet Nam:
	\begin{itemize}
	\item Analyze historical national forest \textbf{inventories} and forest cover maps, 
	\item Pilot \textbf{updated methods} for (1) forest cover and cover change maps, (2) national forest inventory field manual and quality assessment/quality control,
	\item Organize \textbf{participatory workshops} on monitoring systems for local forest activity in
six provinces,
	\end{itemize}
\item Provide \textbf{training} and technical support on forest \textbf{data analysis} and model development with \textbf{R} (Bangladesh, Cambodia, the Philippines, Thailand).
\item Support the design, implementation and update of \textbf{National Forest Inventories} (Bangladesh, Cambodia, Thailand).
\end{itemize}
}

%\cventry{2012--2014}{Forest inventory and biomass assessment expert}{UN-REDD programme, Food and Agriculture Organization of the United Nations}{FAO HQ, Italy}{}{
\cventry{2012--2014}{Forest inventory and biomass assessment expert}{UN-REDD programme}{FAO HQ, Italy}{}{
\begin{itemize}
\item \textbf{Develop allometric equations} to improve UNREDD countries \textbf{forest biomass} estimates, conduct training and develop guidelines and training materials for field work, data exploration and data analysis for developing tree biomass allometric equations (Vietnam, Cambodia, Zambia, Tanzania, Congo, DRC).
\end{itemize}
}

%-----------------------------------------%

\subsection{Research Institutes / NGOs}

\cventry{2011--2012}{Research assistant}{Centre de coopération internationale en recherche agronomique pour le développement (CIRAD)}{Republic of the Congo}{}{
Installation and monitoring of experimental sites, contribution to data analysis and scientific production.}

\cventry{2010}{Research assistant}{Center for international forestry research (CIFOR)}{Madagascar}{6 months}{
Analysis of formal and informal wood supply chain from madagascar east cost.}

\cventry{2009}{Technical assistant}{Groupe energies renouvelables, 
environnement et solidarités \textbf{(GERES)}}{Cambodia}{6 months}{
Wood supply and demand analysis on Phnom Chumriey area.}

\cventry{2008}{Research assistant}{(CIRAD)}{Republic of the Congo}{6 months}{
Study of the nutrient losses by erosion and run off intensity on eucalyptus plantations.}


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\cventry{2006--2010}{Master of forest science}{AgroParisTech-ENGREF}{France}{}{
\begin{itemize}%
	\item \textbf{Sustainable} management of \textbf{tropical} and temperate \textbf{forests}.
	\item Forest and \textbf{climate change} mitigation (MDP, REDD).
	\item \textbf{International policy}, \textbf{economy} and \textbf{sociology} applied to \textbf{natural resources} management.
\end{itemize}
}

\subsection{Masters Thesis}

\cvitem{Title}{\emph{Money Is The Root Of All Evil -- Or Is It?}}
\cvitem{Supervisors}{Professor James Smith \& Associate Professor Jane Smith}
\cvitem{Description}{This thesis explored the idea that money has been the cause of untold anguish and suffering in the world. I found that it has, in fact, not.}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\textmyfont{\section{Experience}}

\subsection{Vocational}

\cventry{2012--Present}{1\textsuperscript{st} Year Analyst}{\textsc{Lehman Brothers}}{Los Angeles}{}{Developed spreadsheets for risk analysis on exotic derivatives on a wide array of commodities (ags, oils, precious and base metals), managed blotter and secondary trades on structured notes, liaised with Middle Office, Sales and Structuring for bookkeeping.
\newline{}\newline{}
Detailed achievements:
\begin{itemize}
\item Learned how to make amazing coffee
\item Finally determined the reason for \textsc{PC LOAD LETTER}:
\begin{itemize}
\item Paper jam
\item Software issues:
\begin{itemize}
\item Word not sending the correct data to printer
\item Windows trying to print in letter format
\end{itemize}
\item Coffee spilled inside printer
\end{itemize}
\item Broke the office record for number of kitten pictures in cubicle
\end{itemize}}

%------------------------------------------------

\cventry{2011--2012}{Summer Intern}{\textsc{Lehman Brothers}}{Los Angeles}{}{Rated "truly distinctive" for Analytical Skills and Teamwork.}

%------------------------------------------------

\subsection{Miscellaneous}

\cventry{2010--2011}{}{}{}{}{Spent some time finding myself. This was a courageous endeavour that didn't have a job title. It was quite important to my overall development though so I'm adding it to my CV. Also it explains the gap in my otherwise stellar CV.}

\cventry{2009--2010}{Computer Repair Specialist}{Buy More}{Burbank}{}{Worked in the Nerd Herd and helped to solve computer problems. Allowed me to become expert in all forms of martial arts and weaponry.}

%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------

\section{Awards}

\cvitem{2011}{School of Business Postgraduate Scholarship}
\cvitem{2010}{Top Achiever Award -- Commerce}

%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Computer skills}

\cvitem{Basic}{\textsc{java}, Adobe Illustrator}
\cvitem{Intermediate}{\textsc{python}, \textsc{html}, \LaTeX, OpenOffice, Linux, Microsoft Windows}
\cvitem{Advanced}{Computer Hardware and Support}

%----------------------------------------------------------------------------------------
%	COMMUNICATION SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Communication Skills}

\cvitem{2010}{Oral Presentation at the California Business Conference}
\cvitem{2009}{Poster at the Annual Business Conference in Oregon}

%----------------------------------------------------------------------------------------
%	LANGUAGES SECTION
%----------------------------------------------------------------------------------------

\section{Languages}

\cvitemwithcomment{English}{Mothertongue}{}
\cvitemwithcomment{Spanish}{Intermediate}{Conversationally fluent}
\cvitemwithcomment{Dutch}{Basic}{Basic words and phrases only}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{Interests}

\renewcommand{\listitemsymbol}{-~} % Changes the symbol used for lists

\cvlistdoubleitem{Piano}{Chess}
\cvlistdoubleitem{Cooking}{Dancing}
\cvlistitem{Running}

%----------------------------------------------------------------------------------------
%	COVER LETTER
%----------------------------------------------------------------------------------------

% To remove the cover letter, comment out this entire block

% \clearpage
% 
% \recipient{HR Department}{Corporation\\123 Pleasant Lane\\12345 City, State} % Letter recipient
% \date{\today} % Letter date
% \opening{Dear Sir or Madam,} % Opening greeting
% \closing{Sincerely yours,} % Closing phrase
% \enclosure[Attached]{curriculum vit\ae{}} % List of enclosed documents
% 
% \makelettertitle % Print letter title
% 
% \lipsum[1-2] % Dummy text
% \lipsum[4] % Dummy text
% 
% \makeletterclosing % Print letter signature
% 
% \newpage


%----------------------------------------------------------------------------------------

\end{document}